---
title: "p8105_hw1_rd3227"
author: "Ruihan Ding"
date: "2025-09-13"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

# Problem 1

Load the moderndive library and the early_january_weather dataset.

```{r}
library(moderndive)
data("early_january_weather")
```

Take a look at the dataset help file.

```{r eval=FALSE}
help("early_january_weather")
```

The early_january_weather dataset contains hourly meteorological data for LGA, JFK and EWR for the month of January 2013. It is a data frame of `r nrow(early_january_weather)` rows representing hourly measurements and `r ncol(early_january_weather)` variables, including `r names(early_january_weather)`. The mean temperature measured in these places during this period is `r mean(early_january_weather$temp)`.

Make a scatterplot of temp vs time_hour, color points using the humid variable and save it to the project directory.

```{r}
ggplot(early_january_weather, aes(x=time_hour, y=temp, color=humid))+geom_point()
ggsave("scatterplot.pdf")
```

Overall, both temperature and humidity show a gradual increasing trend over the course of the dataset. Looking at individual days, it is clear that temperature fluctuates considerably within each day, indicating large daily temperature variations.
